\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{hyperref}

\begin{document}
\title{Project Portfolio Summary}
\author{Nico OR}
\date{}
\maketitle

\section{splisp}
\textit{A copy-free lisp compiler and associated Stack VM}
\begin{itemize}
  \item \textbf{Learning outcomes}
    \begin{itemize}
      \item Implemented a lexer, parser, and semantic analyzer to
        provide a language back end.
      \item Implemented a Stack based Virtual Machine from the Oxford
        specification and extended it with heap instructions to
        support closures.
      \item Implemented a code generator which lowers the abstract
        syntax tree into the Stack's ISA
    \end{itemize}
  \item \textbf{Impact}
    \begin{itemize}
      \item Demonstrates C++ aptitude, working with advanced features
        such as concepts, smart pointers, and a working understanding
        of move semantics.
      \item Demonstrates ability to plan ahead when coding and
        utilize tests to ensure integration of subsystems in the project.
    \end{itemize}
  \item \textbf{Technologies}
    \begin{itemize}
      \item C++
      \item gtest
    \end{itemize}
\end{itemize}

\section{Neural Networks, Haskell, and You}
\textit{On the surprising ergonomics of functional programming for
machine learning}

\begin{itemize}
  \item \textbf{Learning outcomes}
    \begin{itemize}
      \item Implemented a multilayer perceptron from scratch and
        reviewed the math behind training.
      \item Applied functional programming patterns to linear
        algebra-heavy code.
      \item Connected gradient-based optimization theory to a working
        implementation.
    \end{itemize}
  \item \textbf{Impact}
    \begin{itemize}
      \item Demonstrated a working neural network with a clear,
        educational write-up.
    \end{itemize}
  \item \textbf{Technologies}
    \begin{itemize}
      \item Haskell
      \item HMatrix
      \item matplotlib
    \end{itemize}
\end{itemize}

\section{the t-distribution and its consequences}
\textit{Some of the mathematical leg work behind a fundamental statistical tool}

\begin{itemize}
  \item \textbf{Learning outcomes}
    \begin{itemize}
      \item Traced the derivation and intuition behind the
        t-distribution and hypothesis testing.
      \item Connected variance, sampling, and degrees of freedom to
        practical inference.
      \item Strengthened technical exposition of probability concepts.
    \end{itemize}
  \item \textbf{Impact}
    \begin{itemize}
      \item Produced an accessible explanation for students learning
        statistical inference.
    \end{itemize}
  \item \textbf{Technologies}
    \begin{itemize}
      \item Mathematical writing
    \end{itemize}
\end{itemize}

\section{FSAEStats}
\textit{Scalable Analytics for the FSAE student competition}

\begin{itemize}
  \item \textbf{Learning outcomes}
    \begin{itemize}
      \item Evaluated ORM tradeoffs and moved toward a columnar,
        record-batch approach.
      \item Integrated DuckDB with Apache Arrow for efficient query
        and transport.
      \item Streamlined PDF-to-CSV extraction workflows for
        downstream analytics.
    \end{itemize}
  \item \textbf{Impact}
    \begin{itemize}
      \item Delivered a lightweight API for querying FSAE results
        without heavy joins.
      \item Enabled faster analysis by packaging results as Arrow
        record batches.
    \end{itemize}
  \item \textbf{Technologies}
    \begin{itemize}
      \item Rust
      \item DuckDB
      \item Apache Arrow
      \item Camelot (PDF table extraction)
    \end{itemize}
\end{itemize}

\end{document}
